<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{lmer Performance Tips}
%\VignetteDepends{dplyr}
%\VignetteDepends{bbmle}
%\VignetteDepends{numDeriv}
%\VignetteDepends{ggplot2}
%\VignetteDepends{gridExtra}
-->

```{r pkgs,message=FALSE}
library("cricketr")
library("dplyr")
library("ggplot2"); theme_set(theme_bw())
library("bbmle")
```

**fixme**: real `over50.data` won't be available in full package
(need to make fake data)

Here we'll use innings-1 data:
```{r get_data,cache=TRUE}
dd <- filter(over50.data,innings==1)
rr <- get.rtab(dd)  ## get resource table from raw data
nn <- get.ntab(dd)   ## counts per (wicket,over)
```

Different ways of plotting a raw resource table:
```{r plots,warning=FALSE}
## plot(rr0,type="rgl")
p1 <- plot(rr,type="gg_lines",factor_wicket=TRUE)
p2 <- plot(rr,type="gg_lines")
p3 <- plot(rr,type="levelplot")  ## Figure 2.1 from thesis
grid.arrange(p1,p2,p3,nrow=2)
```
Or:
```{r heatmap}
plot(rr,type="heatmap")
```

Compute (and plot) resource surface based on old DL parameters:
```{r DLtab}
dl <- DLtab(DL.par,get.tot(dd))  ## compute DL from 
plot(dl,type="levelplot")
```

Compute weighted RMSE for DL parameters from resource tab:
```{r objfun}
objfun(DL.par,rr,weights=nn,tot.runs=get.tot(dd))
```

Compare `optim`- and `mle2`-based fits:
```{r fit1}
opt1 <- optfun(rr,nn,get.tot(dd))
objfun <- function (p, restab, weights = 1, tot.runs) { 
    weights <- rep(weights, length.out = length(restab))
    predtab <- DLtab(p, tot.runs)
    s <- !is.na(restab) & !is.na(weights) & weights > 0
    -sum(weights[s] *
             dnorm2(restab[s], predtab[s], log = TRUE))/sum(weights[s])
}
parnames(objfun) <- names(DL.par)
m1 <- mle2(minuslogl=objfun,start=DL.par,
     vecpar=TRUE,
     data=list(weights=nn,
               tot.runs=get.tot(dd),
               restab=rr),
     method="L-BFGS-B",
     control=list(parscale=DL.par,maxit=1e5))
all.equal(coef(m1),opt1$par,tol=5e-4)
```

Profiling is possible but slow:
```{r profci,eval=FALSE}
pp <- profile(m1,debug=TRUE)
pp.b <- profile(m1,which="b")
plot(pp.b,show.points=TRUE)
confint(pp.b)
```

Compare new estimates (plus Wald CIs) with old D-L parameters:
```{r plot_comp,echo=FALSE,warning=FALSE}
cc <- confint(m1,method="quad")
mtab <- rbind(
    data.frame(type="newest",
               par=names(coef(m1)),
               est=coef(m1),
               lwr=cc[,1],
               upr=cc[,2]),
    data.frame(type="DL",
               par=names(DL.par),
               est=DL.par,
               lwr=NA,
               upr=NA))
mtab <- transform(mtab,
                  ptype=ifelse(par=="b","b",
                               ifelse(par=="Z0","Z0","F")))
ggplot(mtab,aes(x=par,y=est,ymin=lwr,ymax=upr,colour=type))+
    geom_pointrange()+facet_wrap(~ptype,scale="free")+
        scale_colour_brewer(palette="Set1")
```  

Plot new D-L
```{r newDL}
plot(DLtab(opt1$par,get.tot(dd)),type="gg_lines")
```


## calculate premature stopping times (unfinished)

```{r stoppage_dist}
dd.last <- over50.data %>% group_by(ID,innings) %>%
        filter(totruns==last(totruns)) %>%
            select(ID,wickets,innings,over,totruns) %>%
                arrange(ID)
## regular ending if
##    same numbers of overs in both innings OR
##    all wickets in inning 2 lost (wickets>=9) OR
```
